An asymptotically normal out-of-sample test based on mixed estimation windows

### 2015-04-21 mixedwindow.tex
Add link to bug tracker to main paper

\author{Gray Calhoun\thanks{Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 \nber-\nsf\ Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
    circulated under the name ``An asymptotically normal out-of-sample
  test of equal predictive accuracy for nested models.''}\\%
  Iowa State University}

@@

% \date{March 14, 2013}

>>>>

\author{Gray Calhoun\thanks{Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft http://gray.clhn.org\guillemotright.
    If you find errors or mistakes in this paper, please email me or
    open a new issue at
    \guillemotleft https://git.ece.iastate.edu/gcalhoun/mixedwindow/issues\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 \nber-\nsf\ Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
    circulated under the name ``An asymptotically normal out-of-sample
  test of equal predictive accuracy for nested models.''}\\%
  Iowa State University}

@@
